### 2015-09-19 doc/reports/sandia_final/sandia_final_impact.tex

\label{impact-on-programs}
There are several ongoing projects at the Scientific Computation Research Center (SCOREC) on the RPI campus which AMSI will be used with. Particularly SCOREC's ongoing work on incorporating our dynamic mesh operations with the Albany simulation system developed at Sandia National Labs. For multi-scale simulations using the Albany simulation code, we will make use of AMSI's capabilities to be minimally intrusive and only require modifications at those locations in code where multi-scale terms are needed.

>>>>

\label{impact-on-programs}
There are several ongoing projects at the Scientific Computation Research Center (SCOREC) on the RPI campus which AMSI will be used with. Particularly SCOREC's ongoing work on incorporating our dynamic mesh operations with the Albany simulation system developed at Sandia National Labs. For multi-scale simulations using the Albany simulation code, we will make use of AMSI's capabilities to be minimally intrusive and only require modifications at those locations in code where scale-coupling terms are needed.

### 2015-09-19 doc/reports/sandia_final/sandia_final_introduction.tex

Introduction of influence from scales orders of magnitude removed from the primary scale can take place in several different ways. This influence can be incorporated during the mathematical development of the physical model itself. In this case the multi-scale features are incorporated into the numerical implementation automatically, as a result of their presence in the mathematical model. Multi-scale influences can also be incorporated in a more strictly numerical sense, combining physical models operating at different scales but opera ting on some of the same physical fields and values.

>>>>

Introduction of influence from scales orders of magnitude removed from the primary scale can take place in several different ways. This influence can be incorporated during the mathematical development of the physical model itself. In this case the multi-scale features are incorporated into the numerical implementation automatically, as a result of their presence in the mathematical model. Multi-scale influences can also be incorporated in a more strictly numerical sense, combining physical models operating at different scales but opera ting on some of the same physical fields and values cite{shenoy97} \cite{weinan2003heterogenous}.
